A comparison of single-cell trajectory inference methods: towards more accurate and robust tools

### 2018-03-01 analysis/paper/paper.Rmd
update paper & user guidelines tree

Overall, we find that slingshot predicts the most accurate trajectories across different data sources, trajectory types and metrics, followed by TSCAN and Monocle DDRTree CREF. These results are consistent between real and synthetic datasets CREF, confirming both the relevance of the synthetic data and the accuracy of the real datasets' gold and silver standards. However, results are more variable when comparing the three different evaluation metrics, 
## Detectable trajectory topologies

@@

`r anchor("fig", "implementation_overview")`
![](`r figure_file("implementation_overview.svg", experiment_id="4-method_characterisation")`)
`r ref("fig", "implementation_overview", anchor=TRUE)` First characterization of each method.

@@

<!-- Results  -->

>>>>

Overall, we find that slingshot predicts the most accurate trajectories across different data sources, trajectory types and metrics, followed by TSCAN and Monocle DDRTree CREF. These results are consistent between real and synthetic datasets CREF, confirming both the relevance of the synthetic data and the accuracy of the real datasets' gold and silver standards. However, results are more variable when comparing the three different evaluation metrics, 
##

@@

`r anchor("fig", "implementation_overview")`
![](`r figure_file("method_components.svg", experiment_id="4-method_characterisation")`)
`r ref("fig", "implementation_overview", anchor=TRUE)` First characterization of each method.

@@

<!-- Results  -->
Based on the results of our benchmark, we created a set of practical guidelines for method users `r ref("fig", "user_guidelines")`. The main consideration for the choice of a method is based on the user's existing knowledge about what type of trajectory is expected in the data. If the user expects a linear, cyclic or bifurcating trajectory, a specific set of methods .

`r anchor("fig", "user_guidelines")`
![](`r figure_file("tree.svg", experiment_id="7-user_guidelines")`)
`r ref("fig", "user_guidelines", anchor=TRUE)` Practical guidelines for method users.

### 2018-03-01 analysis/paper/paper_latex.Rmd
update paper & user guidelines tree

`r anchor("fig", "implementation_overview")`
![](`r figure_file("implementation_overview.tmp.pdf", experiment_id="4-method_characterisation")`)
`r ref("fig", "implementation_overview", anchor=TRUE)` First characterization of each method.

@@

<!-- Results  -->

>>>>

`r anchor("fig", "implementation_overview")`
![](`r figure_file("method_components.tmp.pdf", experiment_id="4-method_characterisation")`)
`r ref("fig", "implementation_overview", anchor=TRUE)` First characterization of each method.

@@

<!-- Results  -->
Based on the results of our benchmark, we created a set of practical guidelines for method users `r ref("fig", "user_guidelines")`. The main consideration for the choice of a method is based on the user's existing knowledge about what type of trajectory is expected in the data. If the user expects a linear, cyclic or bifurcating trajectory, a specific set of methods .

`r anchor("fig", "user_guidelines")`
![](`r figure_file("tree.tmp.pdf", experiment_id="7-user_guidelines")`)
`r ref("fig", "user_guidelines", anchor=TRUE)` Practical guidelines for method users.
